---
title: "Scenic analysis in R"
author: "Devika Agarwal"
date: 'Last update: `r date()`'
output:
  html_document:
    theme: cerulean
    number_sections: true
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: yes
      toc_depth: 6
params:
  working_dir: '~/Documents/CNCB/proj009/Vincent_proj009/cellranger/Latest_RMD/Results/SCENIC'
  num_workers: 6 # Number of cores
  datatype: raw # raw or normalised
  results_directory: "./results.dir/pyscenic_r"
  plots_directory: "./plots.dir/pyscenic_r"
  celltype: "celltype" # column name for cell celltype annotations in files or "None"
  condition: "stim" # column name for condition annotation in files or "None"
  celltype_condition: "celltype_stim" # column name for celltype_condition columns in files or "None"
  celltype_zscores: "./auc_zscores_celltype_annotations.csv" # Zscores based on auc for celltypes or "None"
  celltype_stim_zscores: "./auc_zscores_celltype_ann_stim_annotations.csv"  # Zscores based on auc for celltype_stim joint or "None"
  stim_zscores: "./auc_zscores_thirst2_condition_annotations.csv" # Zscores based on auc for condition or "None"
  celltype_zscore_filter_threshold: 3 # Zscore filter threshold for celltype specific scores for heatmap or "None"
  stim_zscore_filter_threshold: 1 # Zscore filter threshold for  condition specific scores for heatmap or "None"
  celltype_stim_zscore_filter_threshold: 4 # Zscore filter threshold for  celltype + condition specific  scores for heatmap or "None"
  binary_mtx: "./binary_matrix.csv" # Binary Auc scores for each cell or "None"
  annotation_celltype: "data.dir/celltype_annotations.csv" # csv file with cellid & celltype annotations for each cell or "None"
  annotation_stim: "data.dir/thirst2_condition_annotations.csv" # csv file with cellid & stim annotation  for each cell or "None"
  annotation_celltype_stim: "data.dir/broad_celltype_stim_annotations.csv" #csv file with cellid & celltype_stim annotation for each cell or "None"
  binary_heatmap_cell_annotations : "data.dir/broad_celltype_annotations.csv" # csv file with cellid and annotation data per cell for binary all cells heatmap or "None"
  rss_celltype: "./broad_celltype_annotations_RSS.csv" # RSS scores per regulon for celltype or "None"
  rss_stim: "./thirst2_condition_annotations_RSS.csv" # RSS scores per regulon for stim or "None"
  rss_celltype_stim: "./broad_celltype_stim_annotations_RSS.csv" # RSS scores per regulon for celltype_stim or "None"
  species: "human" # fly ;human ,mouse or None
  regulon_genes: "./regulons_lucy.csv" #regulon files generatated from Pyscenic pipeline or "None"
  exp_matrix: "data.dir/test.csv" # filtered-raw-expression.csv exp matrix generated in step1 of pipeline for background for pathway analysis or "None"
  go_ont_option: "BP" # "BP", "MF" , "CC" or "ALL" for all three. Default is "MF" in ClusterProfiler
  wilcoxon_celltype_top: "wilcoxon_celltype_top10.csv" #or "None"
  wilcoxon_condition_top: "wilcoxon_condition_reference_top10.csv" # or "None"
  ks_celltype_top: "ks_celltype_top10.csv" # or "None"
  ks_condition_top: "ks_condition_top10.csv" # or "None"
  pvaluecutoff: 0.05 # Pathway enrichment cutoffs
  qvaluecutoff: 0.05 # Pathway enrichment cutoffs
  maxGSSize: 1000 # Pathway enrichment maximum gneset size
  msigdb_geneset: "C2" # geneset category for MSigDB, can be C1: positional gene sets ,C2: curated gene sets,C3: motif gene sets,C4: computational gene sets, C5: GO gene sets,C6: oncogenic signatures,C7: immunologic signatures,H: hallmark gene sets


---
<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 10px;
}
h1.title {
  font-size: 18px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 16px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 16px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 14px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, root.dir= params$working_dir)
# Use the following code to render the document by using objects from the global environment:
# rmarkdown::render("Markdown_code/3a_Thirst2_doublet_identification.Rmd")
```



```{r packages_etc, eval=T}
library(ggplot2)
library(Matrix)
library(cowplot)
library(Seurat)
library(plyr)
library(tidyverse)
library(future)
library(foreach)
library(doMC)
library(uwot)
library(pheatmap)
library(RColorBrewer)
library(tidyr)
library(pheatmap)
library(grid)
library(data.table)
library(ggrepel)
library(readr)
library(clusterProfiler)
library(ReactomePA)
library(foreach)
library(msigdbr)
library(org.Mm.eg.db)
library(org.Hs.eg.db)
try({library(org.Dm.eg.db)})

registerDoMC(cores=params$num_workers)
theme_set(theme_bw())


```

```{r, create_dirs}
results_directory <- params$results_directory
plots_directory <- params$plots_directory
working_dir <- params$working_dir
datatype <- params$datatype
if (!dir.exists(paste0(plots_directory, "/", datatype))) {
    dir.create(paste0(plots_directory, "/", datatype), recursive = TRUE)
}

if (!dir.exists(paste0(results_directory, "/", datatype))) {
    dir.create(paste0(results_directory, "/", datatype), recursive = TRUE)
}


```

```{r functions}
rss_plot = list(
  theme(axis.text.x = element_blank(),axis.ticks.x = element_blank(),axis.title = element_text(size=8),strip.background = element_blank(),panel.background=element_rect(fill="white"), panel.grid.major = element_blank(), strip.text.x = element_text(size=8), panel.grid.minor = element_blank(), axis.text.y = element_text(size=6)))


save_pheatmap_pdf <- function(x, filename, width=7,height=7) {
  stopifnot(!missing(x))
  stopifnot(!missing(filename))
  pdf(filename, width=width, height=height)
  grid::grid.newpage()
  grid::grid.draw(x$gtable)
  dev.off()
}


zscore_heatmap <- function(zscores_df,annotation_type=params$celltype ,filter_threshold=3, plot_height=6, plot_width=8,units="in"){
  if(max(zscores_df$annotation_zscore) >= as.numeric(filter_threshold)){
    zscores_specific <- zscores_df %>% dplyr::filter((annotation_zscore) >= as.numeric(filter_threshold))
    #celltype_zscores_specific %>% ggplot(aes(x=regulon,y=annotation,fill=annotation_zscore)) +geom_rect() + scale_fill_distiller(palette = "YlGnBu", direction=1) + theme_bw()
    zscores_specific_wide <- zscores_specific%>% dplyr::select(regulon, annotation,annotation_zscore) %>% tidyr::pivot_wider(names_from = annotation, values_from = annotation_zscore)
    zscores_specific_wide <- zscores_specific_wide %>% column_to_rownames(var = "regulon")
    zscores_specific_wide <- as.matrix(zscores_specific_wide)
    mat2 <- as.data.frame(zscores_specific_wide)
    mat2 <- mat2 %>%
    mutate_if(is.numeric, round, digits = 1)
    mat2[is.na(mat2)] <- ""
    annotation_type = as.character(annotation_type)
#tiff(filename =paste0('./', annotation,'_regulators_zscores.pdf'), width = 10,height = 6,units = "in", res = 300 )
    plot_1 <- pheatmap(mat= (t(zscores_specific_wide)), color = colorRampPalette((brewer.pal(n = 8, name =
  "YlGnBu")))(100), cluster_cols = F,cluster_rows = F,na_col ="white", display_numbers = as.matrix(t(mat2)), number_format = "%.1f", fontsize_row = 8, legend = T, number_color = "black",fontsize = 8, fontsize_col = 8, main = paste0(annotation_type,' specific TF regulators-Zscore'))
   save_pheatmap_pdf(plot_1, filename = paste0(plots_directory,'/',datatype,'/',annotation_type,'_specific_zscore_',filter_threshold,'_heatmap.pdf'),       width=plot_width,height=plot_height)
   saveRDS(plot_1, file = paste0(plots_directory,'/',datatype,'/',annotation_type,'_specific_zscore_',filter_threshold,'_heatmap.rds'))
#print(plot_1)
#cairo_ps( filename = paste0(plot_path,annotation_type,'specific_zscore_heatmap.eps'), height = plot_height, width = plot_width, onefile = F)
#plot_1
#dev.off()
   print(plot_1)

  }else{
    print("Annotation zscores below the filter threshold parameter")
  }

}

binary_celltype_perc_heatmap <- function(cellInfo_f=params$annotation_celltype, binary_mtx_f=params$binary_mtx, minPerc=0.85, annotation_type ="celltype",plot_height=7,plot_width=10, units="in", cluster_rows=T,cluster_cols=T){
if(annotation_type != "None"){
  cellInfo <- read.csv(cellInfo_f)

  rownames(cellInfo) <- cellInfo$cellid

  cellInfo[,2] <- as.factor(cellInfo[,2])

  binary_mtx <- read_csv(file = binary_mtx_f)
#binary_mtx <- binary_mtx %>% column_to_rownames(var="X1")
#binary_mtx <- (t(binary_mtx))
  minPerc <- minPerc
  #annotation_type <- as.character(annotation_type)
  binary_mtx.merge <- merge(binary_mtx,cellInfo, by.x="X1", by.y="cellid")
  regulon_activity_binarised_celltype <- binary_mtx.merge %>% dplyr::group_by_if(is.factor) %>% dplyr::select(-c(X1)) %>%
  summarise_all(.funs = mean) %>% tibble::column_to_rownames(var = {{annotation_type}})
  regulon_activity_binarised_celltype <- t(regulon_activity_binarised_celltype)
  binaryActPerc_subset <- regulon_activity_binarised_celltype[which(rowSums(regulon_activity_binarised_celltype>minPerc)>0),]
  plot_1 <- pheatmap::pheatmap(binaryActPerc_subset, fontsize = 7,
                   color = colorRampPalette(c("white","pink","red"))(100), breaks=seq(0, 1, length.out = 100),
                   treeheight_row=10, treeheight_col=10, border_color=NA, clustering_method = "ward.D2",cluster_rows=cluster_rows,cluster_cols=cluster_cols)
  save_pheatmap_pdf(plot_1, filename = paste0(plots_directory,'/',datatype,'/',annotation_type,'_regulon_active_perc_cells',minPerc,'_heatmap.pdf'),     width=plot_width,height= plot_height)
  saveRDS(plot_1, file = paste0(plots_directory,'/',datatype,'/',annotation_type,'_regulon_active_perc_cells',minPerc,'_heatmap.rds'))
#print(plot_1)
#cairo_ps( filename = paste0(plot_path,annotation_type,'specific_zscore_heatmap.eps'), height = plot_height, width = plot_width, onefile = F)
#plot_1
#dev.off()
  print(plot_1)

}else{
  print(" annotation csv file not provided")
}

}



binary_auc_heatmap <- function(binary_mtx_f= params$binary_mtx, annotation_col_f=params$binary_heatmap_cell_annotations,plot_height=9, plot_width=12){
 binary_mtx <- read_csv(file =binary_mtx_f)
 binary_mtx <- binary_mtx %>% tibble::column_to_rownames(var= "X1")
 annotation_col <- read.csv(file=annotation_col_f)
 annotation_col <- annotation_col %>% column_to_rownames(var="cellid")
 plot_1 <- pheatmap::pheatmap((t(binary_mtx)), fontsize = 6, color = colorRampPalette((brewer.pal(n = 9, name ="Greys")))(10)
                   ,treeheight_row=10, treeheight_col=10, border_color=NA, clustering_method = "ward.D2", show_rownames = T,fontsize_row =8,      scale="none", show_colnames = F, annotation_col = annotation_col, legend=F)
 save_pheatmap_pdf(plot_1, filename = paste0(plots_directory,'/',datatype,'/','Binary_RegulonActivity_allcells','_heatmap.pdf'),     width=plot_width,height= plot_height)
 saveRDS(plot_1, file = paste0(plots_directory,'/',datatype,'/','Binary_RegulonActivity_allcells','_heatmap.rds'))
 print(plot_1)

}

RSS_annotation_plot <- function(annotation_type=params$celltype,rss_f=params$rss_celltype, units="in", plot_height=5, plot_width=7){
  if(annotation_type!="None"){
    rss_scores <- read_csv(file=rss_f)
    annotation_type <- as.character(annotation_type)
    colnames(rss_scores)[1] <- "annotation"
    rss_scores_long <- rss_scores %>%  tidyr:: pivot_longer(-1,names_to = "Regulon", values_to="RSS") %>%    mutate(across(where(is_character),as_factor))%>% group_by(annotation) %>%  dplyr::arrange(desc(RSS), .by_group=T) %>% mutate(order = row_number())
    rss_scores_long$ID <- paste(rss_scores_long$annotation,"_",rss_scores_long$Regulon,sep="")

    rss_scores_long_2 <- rss_scores %>%  tidyr:: pivot_longer(-1,names_to = "Regulon", values_to="RSS") %>% mutate(across(where(is_character),as_factor))%>% group_by(annotation) %>%  dplyr::arrange(desc(RSS), .by_group=T) %>% mutate(order = row_number()) %>% dplyr::slice(1:5)

    rss_scores_long_2$label <- rss_scores_long_2$Regulon
    rss_scores_long_2$ID <- paste(rss_scores_long_2$annotation,"_",rss_scores_long_2$Regulon,sep="")
    rss_scores_long_2 <- rss_scores_long_2 %>% dplyr::select(ID, label)

    rss_scores_long_final <- merge(rss_scores_long,rss_scores_long_2, by="ID", all.x = T)

    plot_1 <- rss_scores_long_final%>% ggplot(aes(x=order,y=RSS, group=annotation.x)) + geom_point(colour="steelblue")         #scale_y_continuous(limits=c((min(rss_scores_long$RSS)*100/100), (max(rss_scores_long$RSS)*100/100))) +scale_x_continuous(breaks = #rss_scores_long$order, labels = rss_scores_long$Regulon)
    plot_1 <- plot_1 + geom_text_repel( aes(label=label),check_overlap = T,size=2.5) + facet_wrap(~ annotation.x, scales="free") +xlab("Regulon")
    plot_1 <- plot_1 + rss_plot
    plot_1

    ggsave(plot = plot_1,filename=paste0('Top_',annotation_type,'_specific_RSS_plot.pdf'), path= paste0(plots_directory,'/',datatype,'/'),dpi = 300, units =units,height=plot_height, width=plot_width)
    saveRDS(plot_1, file =paste0(plots_directory,'/',datatype,'/','Top_',annotation_type,'_specific_RSS_plot.rds') )
    print(plot_1)
  }else{
    print("No annotation type name string or annotation specific RSS score file provided as input")
  }

}

Num_active_regulons_annotation <- function(cellInfo_f=params$annotation_celltype,binary_mtx_f=params$binary_mtx, annotation_type=params$celltype, units="in", plot_height=3, plot_width=9){
  if(annotation_type !="None"){
    cellInfo <- read.csv(cellInfo_f)
    rownames(cellInfo) <- cellInfo$cellid
    cellInfo[,2] <- as.factor(cellInfo[,2])
    binary_mtx <- read_csv(file = binary_mtx_f)
    annotation_type <- as.character(annotation_type)
    binary_mtx.merge <- merge(binary_mtx,cellInfo, by.x="X1", by.y="cellid")
    active_cells_per_regulon <- binary_mtx.merge %>% dplyr::group_by_if(is.factor) %>% dplyr::select(-c(X1)) %>%
    summarise_all(.funs = sum)
    active_cells_per_regulon_long <- active_cells_per_regulon %>% pivot_longer(-annotation_type, names_to="Regulon", values_to = "N_active_cells")
    nRegulons_per_annotation <- active_cells_per_regulon_long %>% dplyr::group_by(across(1)) %>% summarise(count = sum(N_active_cells>0)) %>% arrange(desc(count))
    colnames(nRegulons_per_annotation)[1] <- "annotation"
    n_annotation_active_per_regulon <- active_cells_per_regulon_long %>% group_by(across(2)) %>% summarise(count= sum(N_active_cells>0))

    p1 <-  ggplot(data=nRegulons_per_annotation, aes(x=reorder(annotation,-count),y=count)) + geom_bar(stat="identity", fill="steelblue") +    xlab(annotation_type) + ylab(paste0('Number of active Regulons per ',annotation_type))+ ggtitle(paste0('Number of active regulons per ',annotation_type)) + barplot_theme
    p1
    ggsave(plot = p1,filename=paste0('barplot_active_regulons_per_',annotation_type,'.pdf'), path= paste0(plots_directory,'/',datatype,'/'),dpi = 300, units =units,height=plot_height, width=plot_width)
    saveRDS(p1, file =paste0(plots_directory,'/',datatype,'/','barplot_active_regulons_per_',annotation_type,'.rds') )
    print(p1)

  }else{
    print("cell type annotation files not provided")
  }

}

Num_annotation_per_regulon <- function(cellInfo_f=params$annotation_celltype,binary_mtx_f=params$binary_mtx, annotation_type=params$celltype, units="in", plot_height=3, plot_width=9){
  if(annotation_type != "None"){
    cellInfo <- read.csv(cellInfo_f)
    rownames(cellInfo) <- cellInfo$cellid
    cellInfo[,2] <- as.factor(cellInfo[,2])
    binary_mtx <- read_csv(file = binary_mtx_f)
    annotation_type <- as.character(annotation_type)
    binary_mtx.merge <- merge(binary_mtx,cellInfo, by.x="X1", by.y="cellid")
    active_cells_per_regulon <- binary_mtx.merge %>% dplyr::group_by_if(is.factor) %>% dplyr::select(-c(X1)) %>%
    summarise_all(.funs = sum)
    active_cells_per_regulon_long <- active_cells_per_regulon %>% pivot_longer(-annotation_type, names_to="Regulon", values_to = "N_active_cells")
    n_annotation_active_per_regulon <- active_cells_per_regulon_long %>% group_by(across(2)) %>% summarise(count= sum(N_active_cells>0))

    p2 <- ggplot(data=n_annotation_active_per_regulon, aes(x=reorder(Regulon,-count),y=count)) + geom_bar(stat="identity", fill="steelblue") +    xlab("Regulons") + ylab(paste0('Number of ', annotation_type, ' active per regulon')) + ggtitle(paste0('Number of ', annotation_type, ' active per regulon')) + barplot_theme
    p2
    ggsave(plot = p2,filename=paste0('barplot_number_of',annotation_type,'active_per_regulon','.pdf'), path= paste0(plots_directory,'/',datatype,'/'),dpi = 300, units =units,height=plot_height, width=plot_width)
    saveRDS(p2, file =paste0(plots_directory,'/',datatype,'/','barplot_number_of',annotation_type,'active_per_regulon','.rds') )

    print(p2)

  }else{
    print("cell type annotation files not provided")
  }

}

barplot_theme <- list(theme(axis.text.x = element_text(angle=45,hjust = 1,vjust =1, size=5),axis.title = element_text(size=6), plot.title = element_text(size=7)))


regulon_pathway_enrichment <- function(regulons_f = params$regulon_gene, ont_option = params$go_ont_option, pathway_db = "enrichGO", maxGSSize = params$maxGSSize, pvalueCutoff = as.numeric(params$pvaluecutoff), qvalueCutoff = as.numeric(params$qvaluecutoff)) {

  regulon_genes <- read_csv(file=regulons_f)
  regulon_genes$genes <- gsub("[[:space:]]", "", regulon_genes$genes) # note

  regulon_genes$genes_list <- (strsplit(regulon_genes$genes, ","))
  genes_list <- (regulon_genes$genes_list)
  names(genes_list) <- regulon_genes$regulon_name

  background <- read_csv(file = params$exp_matrix)
#background <- background[-1,]
  universe <- as.character(background$X1)
  rm(background)
  if (params$species == "fly") {
    res <- compareCluster(geneClusters = genes_list, universe = universe, pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize = maxGSSize, keyType = "SYMBOL", OrgDb = org.Dm.eg.db, readable = F, ont = ont_option , fun = pathway_db)
    if (pathway_db == "enrichGO") {
      res_simplify <- clusterProfiler::simplify(x = res, cutoff = 0.7)
      saveRDS(res_simplify, file = paste0(results_directory, '/', datatype, '/', pathway_db, '_simplified_regulons_results','.rds'))
      return(res_simplify)
    } else {
      saveRDS(res, file = paste0(results_directory, '/', datatype, '/', pathway_db, '_regulons_results', '.rds'))
      return(res)
    }

  } else if(params$species == "human") {
    res <- compareCluster(geneClusters = genes_list, pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize = maxGSSize, keyType = "SYMBOL", OrgDb= org.Hs.eg.db, readable = F, ont = ont_option, fun = pathway_db, universe = universe)
    if (pathway_db == "enrichGO") {
      res_simplify <- clusterProfiler::simplify(x = res, cutoff = 0.7)
      saveRDS(res_simplify, file = paste0(results_directory, '/', datatype, '/', pathway_db, '_simplified_regulons_results', '.rds'))
      return(res_simplify)
    } else {
      saveRDS(res, file = paste0(results_directory, '/', datatype,'/', pathway_db, '_regulons_results','.rds'))
      return(res)
    }

  } else if (params$species == "mouse"){
    res <- compareCluster(geneClusters = genes_list, universe = universe ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize = maxGSSize, fun = pathway_db)
    if (pathway_db == "enrichGO") {
      res_simplify <- clusterProfiler::simplify(x = res, cutoff = 0.7)
      saveRDS(res_simplify, file = paste0(results_directory,'/',datatype,'/', pathway_db,'_simplified_regulons_results','.rds'))
      return(res_simplify)
    } else {
      saveRDS(res,file = paste0(results_directory, '/' ,datatype, '/', pathway_db, '_regulons_results', '.rds'))
      return(res)
    }

  } else if (params$species == "None") {
    print("No species information provided and relevant Organism dbi needs to be loaded from bioconductor")
  } else {
    print("current options are fly, human,mouse or None")
  }

}

enrichplot_theme <- list(theme(legend.title = element_text(size=7), legend.text = element_text(size=7),strip.background = element_blank(), strip.text =   element_text(face= "bold",size=7), axis.text.y = element_text(size=7)))

wilcoxon_pathway_plot <- function(wilcoxon_f=params$wilcoxon_celltype_top,annotation_type="test_cell_type", test_type="one_vs_all", plot_height=8, plot_width=8, units="in", showCategory=8, stat_test="wilcoxon",pathwaydb="GO_term",res_f= GO_res, plot_row=2,plot_col=2){
comparcluster_df <- res_f@compareClusterResult
if(annotation_type != "None"){
   wilcoxon_top10 <- read_csv(file=paste0(results_directory,'/',datatype,'/',wilcoxon_f))
   wilcoxon_top10 <- wilcoxon_top10 %>% dplyr::select(regulon,!!sym(annotation_type))
   cc_subset <- merge(comparcluster_df, wilcoxon_top10, by.x="Cluster", by.y="regulon")
   gsize <- as.numeric(sub("/\\d+$", "", as.character(cc_subset$GeneRatio)))
   gcsize <- as.numeric(sub("^\\d+/", "", as.character(cc_subset$GeneRatio)))
   cc_subset$GeneRatio = gsize/gcsize
   cluster <- paste(as.character(cc_subset$Cluster), "(", gcsize, ")", sep="")
   lv <- unique(cluster)[order(as.numeric(unique(cc_subset$Cluster)))]
   cc_subset$Cluster <- factor(cluster, levels = lv)
   plot_data <- cc_subset %>% group_by(Cluster) %>% dplyr::arrange(p.adjust) %>% dplyr::slice(1:showCategory)

   idx <-  order(plot_data$Cluster)
   plot_data$Description <- factor(plot_data$Description, levels=rev(unique(plot_data$Description[idx])))
   p1 <- ggplot(plot_data, aes_string(x="Cluster",y="Description" ,color="p.adjust"))
   p1 <- p1 + geom_point(aes(size=Count)) + theme(axis.text.y = element_text(size=7), axis.text.x = element_text(size=7, angle = 45, hjust=1))       +scale_color_viridis_c(direction = 1, alpha = 0.8) + xlab("") + ylab("") + theme(legend.title = element_text(size=7), legend.text = element_text(size=7))
   p1 <- p1 + facet_wrap(.~ .data[[annotation_type]], scales="free",shrink=T, nrow = plot_row,ncol = plot_col) +  theme(strip.background = element_blank(), strip.text =   element_text(face= "bold",size=7))
   p1 <- p1 + enrichplot_theme
   ggsave(plot = p1,filename=paste0(pathwaydb, '_plot','_',stat_test,'_top10',annotation_type,'_',test_type,'.pdf'), path= paste0(plots_directory,'/',datatype,'/'),dpi = 300, units =units,height=plot_height, width=plot_width)
    saveRDS(p1, file =paste0(plots_directory,'/',datatype,'/',pathwaydb, '_plot','_',stat_test,'_top10_',annotation_type,'_',test_type,'.rds'))
    print(p1)
}else{
  print("Wilcoxon/KS files cell or condition column name in results file not inputted in function")
}

}


reactome_pathway_enrichment <- function(regulons_f=params$regulon_gene,pathway_db="enrichPathway", maxGSSize=params$maxGSSize,pvalueCutoff= as.numeric(params$pvaluecutoff), qvalueCutoff= as.numeric(params$qvaluecutoff)){

  regulon_genes <- read_csv(file=regulons_f)
  regulon_genes$genes <- gsub("[[:space:]]", "", regulon_genes$genes) # note


  regulon_genes$genes_list <- (strsplit(regulon_genes$genes, ","))
  genes_list <-(regulon_genes$genes_list)
  names(genes_list) <- regulon_genes$regulon_name

  background <- read_csv(file=params$exp_matrix)

#background <- background[-1,]
  if(params$species== "fly"){
    bg_id <- bitr(background$X1, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Dm.eg.db")
    bg_id_v <- as.character(c(bg_id$ENTREZID))
    gene_id_list <- foreach(g=genes_list) %do% {
    id_df_g = bitr(g, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Dm.eg.db")
    id_list_g = as.character(c(id_df_g$ENTREZID))
    }
    names(gene_id_list) <- names(genes_list)
    res <- compareCluster(geneClusters = gene_id_list, universe =bg_id_v ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize =maxGSSize, organism = "fly", readable=T ,fun = pathway_db)
    saveRDS(res,file = paste0(results_directory,'/',datatype,'/',pathway_db ,'_regulons_results','.rds'))
    return(res)
  }else if(params$species == "human"){
    bg_id <- bitr(background$X1, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Hs.eg.db")
    bg_id_v <- as.character(c(bg_id$ENTREZID))
    gene_id_list <- foreach(g=genes_list) %do% {
    id_df_g = bitr(g, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Hs.eg.db")
    id_list_g = as.character(c(id_df_g$ENTREZID))
    }
    names(gene_id_list) <- names(genes_list)
    res <- compareCluster(geneClusters = gene_id_list ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize = maxGSSize, organism="human", readable=T,fun =pathway_db, universe=bg_id_v)
    saveRDS(res,file = paste0(results_directory,'/',datatype,'/',pathway_db,'_regulons_results', '.rds'))
    return(res)
  }else if(params$species == "mouse"){
    bg_id <- bitr(background$X1, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")
    bg_id_v <- as.character(c(bg_id$ENTREZID))
    gene_id_list <- foreach(g=genes_list) %do% {
    id_df_g = bitr(g, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")
    id_list_g = as.character(c(id_df_g$ENTREZID))
    }
    names(gene_id_list) <- names(genes_list)
    res <- compareCluster(geneClusters = gene_list, universe = bg_id_v ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize =maxGSSize, organim="mouse", readable=T,fun = pathway_db)
    saveRDS(res,file = paste0(results_directory,'/',datatype,'/',pathway_db,'_regulons_results','.rds'))
    return(res)
  }else if(params$species=="None"){
    print("No species information provided and relevant Organism dbi needs to be loaded from bioconductor")
  }else{
    print("current options are fly, human,mouse or None")
  }

}




kegg_pathway_enrichment <- function(regulons_f=params$regulon_gene,pathway_db="enrichKEGG", maxGSSize=params$maxGSSize,pvalueCutoff= as.numeric(params$pvaluecutoff), qvalueCutoff= as.numeric(params$qvaluecutoff)){

  regulon_genes <- read_csv(file=regulons_f)
  regulon_genes$genes <- gsub("[[:space:]]", "", regulon_genes$genes) # note


  regulon_genes$genes_list <- (strsplit(regulon_genes$genes, ","))
  genes_list <-(regulon_genes$genes_list)
  names(genes_list) <- regulon_genes$regulon_name

  background <- read_csv(file=params$exp_matrix)

#background <- background[-1,]
  if(params$species== "fly"){
    bg_id <- bitr(background$X1, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Dm.eg.db")
    bg_id_v <- as.character(c(bg_id$ENTREZID))
    gene_id_list <- foreach(g=genes_list) %do% {
    id_df_g = bitr(g, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Dm.eg.db")
    id_list_g = as.character(c(id_df_g$ENTREZID))
    }
    names(gene_id_list) <- names(genes_list)
    res <- compareCluster(geneClusters = gene_id_list, universe =bg_id_v ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize =maxGSSize, organism = "dme" ,fun = pathway_db, keyType="ncbi-geneid")
    saveRDS(res,file = paste0(results_directory,'/',datatype,'/',pathway_db ,'_regulons_results','.rds'))
    return(res)
  }else if(params$species == "human"){
    bg_id <- bitr(background$X1, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Hs.eg.db")
    bg_id_v <- as.character(c(bg_id$ENTREZID))
    gene_id_list <- foreach(g=genes_list) %do% {
    id_df_g = bitr(g, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Hs.eg.db")
    id_list_g = as.character(c(id_df_g$ENTREZID))
    }
    names(gene_id_list) <- names(genes_list)
    res <- compareCluster(geneClusters = gene_id_list ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize = maxGSSize, organism="hsa",fun =pathway_db, universe=bg_id_v, keyType="ncbi-geneid")
    saveRDS(res,file = paste0(results_directory,'/',datatype,'/',pathway_db,'_regulons_results', '.rds'))
    return(res)
  }else if(params$species == "mouse"){
    bg_id <- bitr(background$X1, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")
    bg_id_v <- as.character(c(bg_id$ENTREZID))
    gene_id_list <- foreach(g=genes_list) %do% {
    id_df_g = bitr(g, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")
    id_list_g = as.character(c(id_df_g$ENTREZID))
    }
    names(gene_id_list) <- names(genes_list)
    res <- compareCluster(geneClusters = gene_list, universe = bg_id_v ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize =maxGSSize, organim="mmu",fun = pathway_db, keyType="ncbi-geneid")
    saveRDS(res,file = paste0(results_directory,'/',datatype,'/',pathway_db,'_regulons_results','.rds'))
    return(res)
  }else if(params$species=="None"){
    print("No species information provided and relevant Organism dbi needs to be loaded from bioconductor")
  }else{
    print("current options are fly, human,mouse or None")
  }

}


msigdb_pathway_enrichment <- function(regulons_f=params$regulon_gene,pathway_db="enricher", maxGSSize=params$maxGSSize, pvalueCutoff= as.numeric(params$pvaluecutoff), qvalueCutoff= as.numeric(params$qvaluecutoff),msigdb_geneset=params$msigdb_geneset){

  regulon_genes <- read_csv(file=regulons_f)
  regulon_genes$genes <- gsub("[[:space:]]", "", regulon_genes$genes) # note


  regulon_genes$genes_list <- (strsplit(regulon_genes$genes, ","))
  genes_list <-(regulon_genes$genes_list)
  names(genes_list) <- regulon_genes$regulon_name

  background <- read_csv(file=params$exp_matrix)
#background <- background[-1,]
  universe <- as.character(background$X1)
  rm(background)
  if(params$species== "fly"){
    m_t2g <- msigdbr(species = "Drosophila melanogaster"  , category = msigdb_geneset) %>%
      dplyr::select(gs_name, gene_symbol)
    res <- compareCluster(geneClusters = genes_list, universe = universe ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize =maxGSSize ,fun = "enricher", TERM2GENE= m_t2g)
    saveRDS(res,file = paste0(results_directory,'/',datatype,'/',pathway_db ,'_regulons_results','.rds'))
    return(res)
  }else if(params$species == "human"){
    m_t2g <- msigdbr(species = "Homo sapiens"  , category = msigdb_geneset) %>%
    dplyr::select(gs_name, gene_symbol)
    res <- compareCluster(geneClusters = genes_list, universe = universe ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize =maxGSSize,fun = "enricher", TERM2GENE= m_t2g)
    saveRDS(res,file = paste0(results_directory,'/',datatype,'/',pathway_db ,'_regulons_results','.rds'))
    return(res)

  }else if(params$species == "mouse"){
    m_t2g <- msigdbr(species = "Mus musculus"  , category = msigdb_geneset) %>%
    dplyr::select(gs_name, gene_symbol)
    res <- compareCluster(geneClusters = genes_list, universe = universe ,pAdjustMethod = "BH", pvalueCutoff = pvalueCutoff, qvalueCutoff = qvalueCutoff, maxGSSize =maxGSSize ,fun = "enricher", TERM2GENE= m_t2g)
    saveRDS(res,file = paste0(results_directory,'/',datatype,'/',pathway_db ,'_regulons_results','.rds'))
    return(res)
  }else if(params$species=="None"){
    print("No species information provided and relevant Organism dbi needs to be loaded from bioconductor")
  }else{
    print("current options are fly, human,mouse or None")
  }

}

rss_pathway_plot <- function(rss_f=params$rss_celltype,annotation_type= params$celltype, plot_height=8, plot_width=8, units="in", showCategory=8, pathwaydb="GO_term",res_f= GO_res, plot_row=2,plot_col=2){
  if(annotation_type != "None"){
    comparcluster_df <- res_f@compareClusterResult
    rss_scores <- read_csv(file=rss_f)
    annotation_type <- as.character(annotation_type)
    colnames(rss_scores)[1] <- "annotation"
    rss_scores_long <- rss_scores %>%  tidyr:: pivot_longer(-1,names_to = "Regulon", values_to="RSS") %>%    mutate(across(where(is_character),as_factor))%>% group_by(annotation) %>%  dplyr::arrange(desc(RSS), .by_group=T) %>% dplyr::slice(1:10) %>% dplyr::select(annotation,Regulon)
   cc_subset <- merge(comparcluster_df, rss_scores_long, by.x="Cluster", by.y="Regulon")
   gsize <- as.numeric(sub("/\\d+$", "", as.character(cc_subset$GeneRatio)))
   gcsize <- as.numeric(sub("^\\d+/", "", as.character(cc_subset$GeneRatio)))
   cc_subset$GeneRatio = gsize/gcsize
   cluster <- paste(as.character(cc_subset$Cluster), "(", gcsize, ")", sep="")
   lv <- unique(cluster)[order(as.numeric(unique(cc_subset$Cluster)))]
   cc_subset$Cluster <- factor(cluster, levels = lv)
   plot_data <- cc_subset %>% group_by(Cluster) %>% dplyr::arrange(p.adjust) %>% dplyr::slice(1:7)
   idx <-  order(plot_data$Cluster)
   plot_data$Description <- factor(plot_data$Description, levels=rev(unique(plot_data$Description[idx])))
   p1 <- ggplot(plot_data, aes_string(x="Cluster",y="Description" ,color="p.adjust"))
   p1 <- p1 + geom_point(aes(size=Count)) + theme(axis.text.y = element_text(size=7), axis.text.x = element_text(size=7, angle = 45, hjust=1))       +scale_color_viridis_c(direction = 1, alpha = 0.8) + xlab("") + ylab("") + theme(legend.title = element_text(size=7), legend.text = element_text(size=7))
   p1 <- p1 + facet_wrap(.~ annotation, scales="free",shrink=T, nrow = plot_row,ncol = plot_col) +  theme(strip.background = element_blank(), strip.text =   element_text(face= "bold",size=7))
   p1 <- p1 + enrichplot_theme
   ggsave(plot = p1,filename=paste0(pathwaydb, '_plot','_','RSS_scores','_top10',annotation_type,'.pdf'), path= paste0(plots_directory,'/',datatype,'/'),dpi = 300, units =units,height=plot_height, width=plot_width)
    saveRDS(p1, file =paste0(plots_directory,'/',datatype,'/',pathwaydb, '_plot','_','RSS_Scores','_top10_',annotation_type,'.rds'))
    print(p1)
  }else{
    print("annotation type not inputted")
  }

}


```



```{r, eval=T}
#load(params$seurat_object)
#auc_output <- read.csv(file= params$auc_output,header=T)
#celltype_zscores <- read.csv(file=params$celltype_zscores, header=T)
#celltype_stim_zscores <- read.csv(file=params$celltype_stim_zscores,header=T)

```


# Celltype or annotation  specific heatmaps based on Zscores

## Celltype

```{r,fig.height=8, fig.width=8}
# "annotation_type" in function giving the type of annotation : options : celltype, stim or celltype_stim
if(params$celltype != "None"){
  celltype_zscores <- read.csv(file=params$celltype_zscores,header=T)
  zscore_heatmap(zscores_df = celltype_zscores,plot_height = 9,plot_width = 8, filter_threshold = params$celltype_zscore_filter_threshold, annotation_type = params$celltype)
} else {
  print("No celltypes were provided")
}


```

## Celltype + Condition

```{r,fig.height=15, fig.width=10}
# "annotation_type" in function giving the type of annotation : options : celltype, stim or celltype_stim
if(params$celltype_condition != "None"){
  celltype_stim_zscores <- read.csv(file=params$celltype_stim_zscores,header=T)
  zscore_heatmap(zscores_df = celltype_stim_zscores,plot_height = 15,plot_width = 10, annotation_type = params$celltype_condition,filter_threshold = params$celltype_stim_zscore_filter_threshold)
} else {
  print("No celltype + condition zscore file provided")
}

```


## Condition

```{r}
# "annotation_type" in function giving the type of annotation : options : celltype, stim or celltype_stim
if(params$condition != "None" & params$stim_zscore_filter_threshold !="None"){
  stim_zscores <- read.csv(file=params$stim_zscores,header=T)
  zscore_heatmap(zscores_df = stim_zscores,plot_height = 6,plot_width = 9, annotation_type = params$condition,filter_threshold = params$stim_zscore_filter_threshold)
} else {
  print("No condition only zscore file provided")
}

```

# Celltype or annotation  specific heatmaps based on binarisation matrix

 + Binarized version (~ percentage of cells of that *cell type/cluster* with the regulon *active* or *on*)

## Celltype

```{r, fig.height=9,fig.width=12}
# "annotation_type" in function giving the type of annotation : options : celltype, stim or celltype_stim . This is based on the  2nd column name in params$annotation_celltype file
if(params$celltype != "None"){
  binary_celltype_perc_heatmap(cellInfo_f=params$annotation_celltype, binary_mtx_f=params$binary_mtx, minPerc=0.70, annotation_type =params$celltype,plot_height=7,plot_width=10, units="in")
} else{
  print("No celltype information provided in the parameters so analysis not run")
}


```

## Condition

```{r, fig.height=4,fig.width=6}
# "annotation_type" in function giving the type of annotation : options : celltype, stim or celltype_stim . This is based on the  2nd column name in params$annotation_stim file
if(params$condition != "None"){
  binary_celltype_perc_heatmap(plot_height = 4,plot_width = 6, annotation_type = params$condition,cellInfo_f =params$annotation_stim, minPerc = .60,cluster_rows=F,cluster_cols=F)

} else{
  print("No condition information provided in the parameters")
}

```

## Cell + Condition

```{r, fig.height=6,fig.width=8}
# "annotation_type" in function giving the type of annotation : options : celltype, stim or celltype_stim . This is based on the  2nd column name in params$annotation_celltype_stim file
if(params$celltype_condition != "None"){
  binary_celltype_perc_heatmap(plot_height = 10,plot_width = 15, annotation_type = params$celltype_condition,cellInfo_f =params$annotation_celltype_stim, minPerc = .70)
} else{
  print("No celltype + condition information provided in the parameters")
}

```

# Binary AUC score Heatmap

```{r, fig.width=12, fig.height=11}
binary_auc_heatmap(annotation_col_f = params$binary_heatmap_cell_annotations, plot_height=10,binary_mtx_f = params$binary_mtx)
```


# RSS score based regulons

## Cell-type specific

```{r, fig.height=6, fig.width=8}
# annotation_type is used to name saved plots and RDS objects, can be anything the user wants
if(params$celltype != "None"){
  RSS_annotation_plot(annotation_type = params$celltype,rss_f = params$rss_celltype,units = "in",plot_height = 6,plot_width = 8)
} else{
  print("No celltype information provided")
}


```

## Condition specific

```{r, fig.height=3, fig.width=4}
# annotation_type is used to name saved plots and RDS objects, can be anything the user wants
if(params$condition != "None"){
  RSS_annotation_plot(annotation_type = params$condition,rss_f = params$rss_stim,units = "in",plot_height = 4,plot_width = 5)
} else{
  print("No condition specific information provided")
}


```

## Celltype + condition specific


```{r, fig.height=8, fig.width=10}
# annotation_type is used to name saved plots and RDS objects, can be anything the user wants
if(params$celltype_condition != "None"){
  RSS_annotation_plot(annotation_type = params$celltype_condition,rss_f = params$rss_celltype_stim,units = "in",plot_height = 12,plot_width = 12)
} else{
  print("No celltype + condition information provided")
}

```

# Binary Regulon activity summary

## Celltypes

```{r, fig.width=10, fig.height=3}
# annotation_type has to be "celltype"
if(params$celltype != "None"){
  Num_active_regulons_annotation(cellInfo_f = params$annotation_celltype,binary_mtx_f = params$binary_mtx,annotation_type = params$celltype,units = "in",plot_height = 4,plot_width = 12)

  Num_annotation_per_regulon(cellInfo_f = params$annotation_celltype,binary_mtx_f = params$binary_mtx,annotation_type = params$celltype,units = "in",plot_height = 4,plot_width = 11)

} else{
  print ("No celltype information provided")
}



```

## Condition

```{r}
# annotation_type has to be "stim"
if(params$condition != "None"){
  Num_active_regulons_annotation(cellInfo_f = params$annotation_stim, binary_mtx_f = params$binary_mtx,annotation_type =params$condition,units = "in",plot_height = 3,plot_width = 4)
}

```

```{r, fig.height=4, fig.width=10}
# annotation_type has to be "stim"
if(params$condition != "None"){
  Num_annotation_per_regulon(cellInfo_f = params$annotation_stim,binary_mtx_f = params$binary_mtx,annotation_type = params$condition,units = "in",plot_height = 4,plot_width = 11)
}

```

## Celltype + Condition

```{r, fig.width=5, fig.height=2}
# annotation_type has to be "celltype_stim"
if(params$celltype_condition != "None"){
  Num_active_regulons_annotation(cellInfo_f = params$annotation_celltype_stim,binary_mtx_f = params$binary_mtx,annotation_type =params$celltype_condition,units = "in",plot_height = 3,plot_width = 6 )
}

```

```{r, fig.height=3, fig.width=10}
# annotation_type has to be "celltype_stim"
if(params$celltype_condition != "None"){
  Num_annotation_per_regulon(cellInfo_f = params$annotation_celltype_stim,binary_mtx_f = params$binary_mtx,annotation_type = params$celltype_condition,units = "in",plot_height = 4,plot_width = 11)
}

```

# Gene Over-representation analysis of Regulon target genes


## GO Biological Process

```{r}
GO_res <- regulon_pathway_enrichment(regulons_f = params$regulon_genes, ont_option = params$go_ont_option, pathway_db = "enrichGO", maxGSSize = params$maxGSSize)


```

### Top 10 wilcoxon regulons by celltype (one vs all)

```{r, fig.height=7, fig.width=8}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$celltype != "None"){
  wilcoxon_pathway_plot(wilcoxon_f = params$wilcoxon_celltype_top,annotation_type="test_cell_type", test_type="one_vs_all", plot_height=10, plot_width=11, units="in", showCategory = 7,stat_test = "wilcoxon",pathwaydb = "GO_term",res_f = GO_res, plot_row = 5,plot_col = 4)
}


```

### Top 10 wilcoxon regulons by condition (Reference)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$condition != "None"){
  wilcoxon_pathway_plot(wilcoxon_f =params$wilcoxon_condition_top,annotation_type="test_condition", test_type="reference", plot_height=6, plot_width=8, units="in", showCategory = 7,stat_test = "wilcoxon",pathwaydb = "GO_term",res_f = GO_res,plot_row = 0,plot_col = 2)
}

```

### Top 10 KS regulons by celltype (one vs all)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$celltype != "None"){
  wilcoxon_pathway_plot(wilcoxon_f =params$ks_celltype_top, annotation_type ="test", test_type="one_vs_all", plot_height=7, plot_width=10, units="in", showCategory = 7,stat_test = "KS_celltype",pathwaydb = "GO_term",res_f = GO_res,plot_col = 5,plot_row = 4)
}

```


### Top 10 KS test regulons by condition (reference)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$condition != "None"){
  wilcoxon_pathway_plot(wilcoxon_f =params$ks_condition_top, annotation_type = "test", test_type="reference", plot_height=7, plot_width=10, units="in", showCategory = 7,stat_test = "KS_condition",pathwaydb = "GO_term",res_f = GO_res,plot_row = 0,plot_col = 4)
}

```



### Top 10 RSS Regulons (celltype)

```{r, fig.height=8,fig.width=10}
if(params$celltype != "None"){
  rss_pathway_plot(rss_f = params$rss_celltype,annotation_type = params$celltype,showCategory = 8,pathwaydb = "GO_term",res_f = GO_res,plot_height = 8,plot_width = 10,units = "in",plot_row = 5,plot_col = 4)
}


```

### Top 10 RSS Regulons (condition)

```{r, fig.height=6,fig.width=8}
if(params$condition != "None"){
  rss_pathway_plot(rss_f = params$rss_stim,annotation_type = params$condition,showCategory = 8,pathwaydb = "GO_term",res_f = GO_res,plot_height = 6,plot_width = 8,units = "in",plot_row = 2,plot_col = 4)
}




```

### Top 10 RSS Regulons (celltype + condition)


```{r, fig.height=8,fig.width=10, eval=T}
if(params$celltype_condition != "None"){
  rss_pathway_plot(rss_f = params$rss_celltype_stim,annotation_type = params$celltype_condition,showCategory = 8,pathwaydb = "GO_term",res_f = GO_res,plot_height = 8,plot_width = 10,units = "in",plot_row = 7,plot_col = 5)
}



```



## Reactome pathways

```{r}
Reactome_res <- reactome_pathway_enrichment(regulons_f = params$regulon_genes,pathway_db = "enrichPathway",maxGSSize = params$maxGSSize)

```

### Top 10 wilcoxon regulons by celltype (one vs all)

```{r, fig.height=8, fig.width=8}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$celltype != "None"){
  wilcoxon_pathway_plot(wilcoxon_f = params$wilcoxon_celltype_top,annotation_type="test_cell_type", test_type="one_vs_all", plot_height=10, plot_width=11, units="in", showCategory = 7,stat_test = "wilcoxon",pathwaydb = "Reactome",res_f = Reactome_res,plot_row = 5,plot_col = 4)
}


```

### Top 10 wilcoxon regulons by condition (Reference)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$condition != "None") {
  wilcoxon_pathway_plot(wilcoxon_f =params$wilcoxon_condition_top,annotation_type="test_condition", test_type="reference", plot_height=6, plot_width=8, units="in", showCategory = 7,stat_test = "wilcoxon",pathwaydb = "Reactome",res_f = Reactome_res)
}

```

### Top 10 KS regulons by celltype (one vs all)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$celltype != "None"){
  wilcoxon_pathway_plot(wilcoxon_f =params$ks_celltype_top, annotation_type = "test", test_type="one_vs_all", plot_height=7, plot_width=10, units="in", showCategory = 7,stat_test = "KS_celltype",pathwaydb = "Reactome",res_f = Reactome_res,plot_row = 5,plot_col = 4)
}

```


### Top 10 KS test regulons by condition (reference)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$condition != "None"){
  wilcoxon_pathway_plot(wilcoxon_f =params$ks_condition_top, annotation_type ="test", test_type="reference", plot_height=7, plot_width=10, units="in", showCategory = 7,stat_test = "KS_condition",pathwaydb = "Reactome",res_f = Reactome_res)
}

```


### Top 10 RSS Regulons (celltype)

```{r, fig.height=8,fig.width=10}
if(params$celltype != "None"){
 rss_pathway_plot(rss_f = params$rss_celltype,annotation_type = params$celltype,showCategory = 8,pathwaydb = "Reactome",res_f = Reactome_res,plot_height = 8,plot_width = 10,units = "in",plot_row = 5,plot_col = 4)
}




```

### Top 10 RSS Regulons (condition)

```{r, fig.height=6,fig.width=8}
if(params$condition != "None") {
  rss_pathway_plot(rss_f = params$rss_stim,annotation_type = params$condition,showCategory = 8,pathwaydb = "Reactome",res_f = Reactome_res,plot_height = 6,plot_width = 8,units = "in",plot_row = 2,plot_col = 4)
}




```

### Top 10 RSS Regulons (celltype + condition)

```{r, fig.height=8,fig.width=10, eval=T}
if(params$celltype_condition != "None"){
  rss_pathway_plot(rss_f = params$rss_celltype_stim,annotation_type = params$celltype_condition,showCategory = 8,pathwaydb = "Reactome",res_f = Reactome_res,plot_height = 8,plot_width = 10,units = "in",plot_row = 7,plot_col = 5)

}



```





## MsigDB C2 curated pathways

```{r}
msigdb_c2_res <- msigdb_pathway_enrichment(regulons_f = params$regulon_genes,pathway_db = "enricher",maxGSSize = params$maxGSSize, msigdb_geneset = params$msigdb_geneset)


```

### Top 10 wilcoxon regulons by celltype (one vs all)

```{r, fig.height=7, fig.width=8}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$celltype != "None"){
  wilcoxon_pathway_plot(wilcoxon_f = params$wilcoxon_celltype_top,annotation_type="test_cell_type", test_type="one_vs_all", plot_height=10, plot_width=11, units="in", showCategory = 7,stat_test = "wilcoxon",pathwaydb = "msigdb_curated",res_f = msigdb_c2_res, plot_row = 5,plot_col = 4)
}

```

### Top 10 wilcoxon regulons by condition (Reference)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$condition != "None") {
  wilcoxon_pathway_plot(wilcoxon_f =params$wilcoxon_condition_top,annotation_type="test_condition", test_type="reference", plot_height=6, plot_width=8, units="in", showCategory = 7,stat_test = "wilcoxon",pathwaydb = "msigdb_curated",res_f = msigdb_c2_res,plot_row = 0,plot_col = 2)
}

```

### Top 10 KS regulons by celltype (one vs all)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$celltype != "None") {
  wilcoxon_pathway_plot(wilcoxon_f =params$ks_celltype_top, annotation_type ="test", test_type="one_vs_all", plot_height=7, plot_width=10, units="in", showCategory = 7,stat_test = "KS_celltype",pathwaydb = "msigdb_curated",res_f = msigdb_c2_res,plot_col = 5,plot_row = 4)
}

```


### Top 10 KS test regulons by condition (reference)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$condition != "None"){
  wilcoxon_pathway_plot(wilcoxon_f =params$ks_condition_top, annotation_type = "test", test_type="reference", plot_height=7, plot_width=10, units="in", showCategory = 7,stat_test = "KS_condition",pathwaydb = "msigdb_curated",res_f = msigdb_c2_res,plot_row = 0,plot_col = 4)
}

```


### Top 10 RSS Regulons (celltype)

```{r, fig.height=8,fig.width=10}
if(params$celltype != "None"){
  rss_pathway_plot(rss_f = params$rss_celltype,annotation_type = params$celltype,showCategory = 8,pathwaydb = "msigdb_curated",res_f = msigdb_c2_res,plot_height = 8,plot_width = 10,units = "in",plot_row = 5,plot_col = 4)
}


```

### Top 10 RSS Regulons (condition)

```{r, fig.height=6,fig.width=8}
if(params$condition != "None"){
  rss_pathway_plot(rss_f = params$rss_stim,annotation_type = params$condition,showCategory = 8,pathwaydb = "msigdb_curated",res_f = msigdb_c2_res,plot_height = 6,plot_width = 8,units = "in",plot_row = 2,plot_col = 4)
}



```

### Top 10 RSS Regulons (celltype + condition)

```{r, fig.height=8,fig.width=10, eval=T}
if(params$celltype_condition != "None") {
  rss_pathway_plot(rss_f = params$rss_celltype_stim,annotation_type = params$celltype_condition,showCategory = 8,pathwaydb = "msigdb_curated",res_f = msigdb_c2_res,plot_height = 8,plot_width = 10,units = "in",plot_row = 7,plot_col = 4)

}



```


## KEGG pathways

```{r}
KEGG_res <- kegg_pathway_enrichment(regulons_f = params$regulon_genes,pathway_db = "enrichKEGG",maxGSSize = params$maxGSSize)

```

### Top 10 wilcoxon regulons by celltype (one vs all)

```{r, fig.height=8, fig.width=8}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$celltype != "None"){
  wilcoxon_pathway_plot(wilcoxon_f = params$wilcoxon_celltype_top,annotation_type="test_cell_type", test_type="one_vs_all", plot_height=10, plot_width=11, units="in", showCategory = 7,stat_test = "wilcoxon",pathwaydb = "KEGG",res_f = KEGG_res,plot_row = 5,plot_col = 4)
}


```

### Top 10 wilcoxon regulons by condition (Reference)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$condition != "None"){
  wilcoxon_pathway_plot(wilcoxon_f =params$wilcoxon_condition_top,annotation_type="test_condition", test_type="reference", plot_height=6, plot_width=8, units="in", showCategory = 7,stat_test = "wilcoxon",pathwaydb = "KEGG",res_f = KEGG_res)
}

```

### Top 10 KS regulons by celltype (one vs all)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$celltype != "None"){
  wilcoxon_pathway_plot(wilcoxon_f =params$ks_celltype_top, annotation_type = "test", test_type="one_vs_all", plot_height=7, plot_width=10, units="in", showCategory = 7,stat_test = "KS_celltype",pathwaydb = "KEGG",res_f = KEGG_res,plot_row = 5,plot_col = 4)
}

```


### Top 10 KS test regulons by condition (reference)


```{r,fig.height=4, fig.width=6}
# annotation_type is the column names from wilcoxon or KS results file with cell type or condition annotation
if(params$condition != "None"){
  wilcoxon_pathway_plot(wilcoxon_f =params$ks_condition_top, annotation_type ="test", test_type="reference", plot_height=7, plot_width=10, units="in", showCategory = 7,stat_test = "KS_condition",pathwaydb = "KEGG",res_f = KEGG_res)
}

```

### Top 10 RSS Regulons (celltype)

```{r, fig.height=8,fig.width=10}
if(params$celltype!= "None"){
  rss_pathway_plot(rss_f = params$rss_celltype,annotation_type = params$celltype,showCategory = 8,pathwaydb = "KEGG",res_f = KEGG_res,plot_height = 8,plot_width = 10,units = "in",plot_row = 5,plot_col = 4)
}



```

### Top 10 RSS Regulons (condition)

```{r, fig.height=6,fig.width=8}
if(params$condition != "None"){
  rss_pathway_plot(rss_f = params$rss_stim,annotation_type = params$condition,showCategory = 8,pathwaydb = "KEGG",res_f = KEGG_res,plot_height = 6,plot_width = 8,units = "in",plot_row = 2,plot_col = 4)

}



```

### Top 10 RSS Regulons (celltype + condition)

```{r, fig.height=8,fig.width=10,eval=T}
if(params$celltype_condition != "None"){
  rss_pathway_plot(rss_f = params$rss_celltype_stim,annotation_type = params$celltype_condition,showCategory = 8,pathwaydb = "KEGG",res_f = KEGG_res,plot_height = 8,plot_width = 10,units = "in",plot_row = 7,plot_col = 4)

}



```


# Session info

```{r session_info}
sessionInfo()
```
